Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-22 paper/structureScene.tex
definition of y_1 is unnecessary.

\subsection{Invariance and stability in acoustic scene classification}
The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training the classifier.
From any set of descriptors -- \eg the time-frequency representation $\boldsymbol{x_1}(t,\gamma_1)$ of  a signal $\boldsymbol{x}(t)$ --
a translation-invariant representation up to time skills of duration $T$ can be simply obtained
by convolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency
set to $1/T$:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma_1) = (\boldsymbol{x_1} \ast \boldsymbol{\phi}) (t).
\end{equation}
As a downside, the transient information in $\boldsymbol{x_1}$ at finer scales than $T$ are lost by this low-pass filtering, hence a lack of discriminability in feature space.
To address this issue, the temporal scattering transform recovers this information by convolving $x_1$ with wavelets whose center frequencies are above $1/T$ and subsequently applying complex modulus.

@@

The wavelet transform $\boldsymbol{}$ of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelets:
$\boldsymbol{y_1}(t, \gamma_1) =
(\boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}})(t)$.
Applying pointwise complex modulus to $\boldsymbol{y_1}$ yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{y_1}(t, \gamma_1)\vert
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t).
\end{equation}
The wavelet scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the CQT has a fixed temporal resolution, constrained by the support of the STFT analyzing window.
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost.
This property allows to observe amplitude modulations at fine temporal scales in the scalogram, down to the minimum scale $2Q_1/\xi_1$ for $\gamma = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$.

>>>>

\subsection{Invariance and stability in acoustic scene classification}
The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training the classifier.
From any set of descriptors -- \eg the time-frequency representation $\boldsymbol{x_1}(t,\gamma_1)$ of  a signal $\boldsymbol{x}(t)$ --
a translation-invariant representation up to time skills of duration $T$ can be simply obtained
by convolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency
set to $1/T$:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma_1) = (\boldsymbol{x_1} \ast \boldsymbol{\phi}) (t).
\end{equation}
As a downside, the transient information in $\boldsymbol{x_1}$ at finer scales than $T$ are lost by this low-pass filtering, hence a lack of discriminability in feature space.
To address this issue, the temporal scattering transform recovers this information by convolving $\boldsymbol{x_1}$ with wavelets whose center frequencies are above $1/T$, and subsequently applying complex modulus.

@@

The wavelet transform $\boldsymbol{}$ of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelets.
Applying pointwise complex modulus to $\boldsymbol{y_1}$ yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t).
\end{equation}
The wavelet scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the CQT has a fixed temporal resolution, constrained by the support of the STFT analyzing window.
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost.
This property allows to observe amplitude modulations at fine temporal scales in the scalogram, down to the minimum scale $2Q_1/\xi_1$ for $\gamma = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$.
